Extensibility and Composability of Multi-Stencil Domain Specific Frameworks

### 2017-03-07 ARTICLES/IJPP/articleR1/evaluation.tex
relecture + todo

In this section we propose an evaluation of the fusion optimization. From the $TSP$ tree computed by MSC it is possible, according to specific conditions, to merge domain loops of kernels, thus optimizing the use of cache memories. This optimization is called a fusion and has been introduced in Section\ref{sect:fusion}. Three fusion optimizations
%\CP{les rappeler !}
%
have been formally detailed in Section~\ref{sect:fusion}. The two first one of Figures~\ref{fig:fus1} and~\ref{fig:fus2} have been automatically detected by MSF in our case study (\ie scatter optimization has not been detected).

Figure~\ref{fig:fusion} shows the number of iterations per second as a function of the number of cores with and without fusions. This benchmark is performed on FullSWOF2D onto a $500 \times 500$ domain size with $200$ time iterations, and by using data parallelism alone (without tasks). As explained in Section~\ref{sect:fusion}, the MSF loop fusion happens at a high level. Most of the time such fusions are done naturally by a computer scientist. However, an automatic detection of such fusions avoids errors, particularly for a parallel execution. In addition to this, more advanced fusion cases, such as a scatter are more difficult to deduce. In FullSWOF2D a total of  62 fusions are proposed by MSF over a total of 98 computation kernels. Figure~\ref{fig:fusion} shows that the performance is clearly improved (around 40\%) by these fusions.

@@

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout2_close_median.pdf}
  \caption{String scaling on a 500x500 domain size with $200$ time iterations. Blue curves represent strong scaling for data parallelism with and without fusion. Red curves represent strong scaling by using 2 cores per MPI process dedicated to tasks, with and without fusion.}
  \label{fig:fusion1}
  %\CP{A FINIR !!! ERREUR DANS LEGENDES AUSSI. COULEUR PROCHES}
\end{center}\end{figure}

@@

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout8_close_median.pdf}
  \caption{String scaling on a 500x500 domain size with $200$ time iterations. Blue curves represent strong scaling for data parallelism with and without fusion, thus are exactly the same than blue curves of Fig.~\ref{fig:fusion1}. Red curves represent strong scaling by using 8 cores per MPI process dedicated to tasks, with and without fusion.}
  \label{fig:fusion2}
    %\CP{A FINIR !!! ERREUR DANS LEGENDES AUSSI.}
\end{center}\end{figure}
As a result, if fusion optimization incurs a too large reduction of the number of tasks to feed dedicated cores, the problem observed for 16 cores in Figure~\ref{fig:close} happens earlier which reduces obtained performances. For this reason, MSF performs fusions only when data parallelization is used alone. This choice could be more intelligent but this is the subject of future work.

>>>>

In this section we propose an evaluation of the fusion optimization. From the $TSP$ tree computed by MSC it may be possible, according to some specific conditions, to merge the domain loops of some kernels, thus optimizing the use of cache memories. This optimization is called a fusion and has been introduced in Section\ref{sect:fusion}. Three fusion optimizations
%\CP{les rappeler !}
%
have been formally detailed in Section~\ref{sect:fusion}. The two first ones of Figures~\ref{fig:fus1} and~\ref{fig:fus2}~\vpageref{fig:fus2} have been automatically detected by MSF in our case study (\ie scatter optimization has not been detected).
\CP{Et la troisieme ?}

Figure~\ref{fig:fusion} shows the number of iterations per second as a function of the number of cores with and without fusions. This benchmark is performed on FullSWOF2D onto a $500 \times 500$ domain size with $200$ time iterations, and by using data parallelism alone (without tasks). As explained in Section~\ref{sect:fusion}, the MSF loop fusion happens at a high level. Most of the time such fusions are done naturally by a computer scientist. However, an automatic detection of such fusions avoids errors, particularly for a parallel execution. In addition to this, more advanced fusion cases, such as a scatter, are more difficult to deduce. In FullSWOF2D a total of  62 fusions are proposed by MSF over a total of 98 computation kernels. Figure~\ref{fig:fusion} shows that the performance is clearly improved (around 40\%) by these fusions.

@@

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout2_close_median.pdf}
  \caption{Strong scaling on a 500x500 domain size with $200$ time iterations. Blue curves represent strong scaling for data parallelism with and without fusion. Red curves represent strong scaling by using 2 cores per MPI process dedicated to tasks, with and without fusion.}
  \label{fig:fusion1}
  \CP{ERREUR DANS LEGENDES !!}
\end{center}\end{figure}

@@

\begin{figure}[!h]\begin{center}
  \includegraphics[width=.6\textwidth]{../results/task_scaling/500_200/withwithout8_close_median.pdf}
  \caption{Strong scaling on a 500x500 domain size with $200$ time iterations. Blue curves represent strong scaling for data parallelism with and without fusion, thus are exactly the same than blue curves of Fig.~\ref{fig:fusion1}. Red curves represent strong scaling by using 8 cores per MPI process dedicated to tasks, with and without fusion.}
  \label{fig:fusion2}
    \CP{ERREUR DANS LEGENDES.}
\end{center}\end{figure}
In conclusion, if fusion optimization incurs a too large reduction of the number of tasks to feed dedicated cores, the problem observed for 16 cores in Figure~\ref{fig:close} happens earlier which reduces performance. For this reason, MSF performs fusions only when data parallelization is used alone. This choice could be more intelligent but this is the subject of future work.
